\vspace{-15mm}\fontsize{16pt}{10pt}\selectfont\textbf{Facial Expression Recognition with\\ Convolutional Neural Networks}

### 2018-04-14 doc/paper.tex
figures

@@

\begin{figure}[H]
	\includegraphics[width=0.48\textwidth]{class_dist}
	\caption{FER-2013 emotion class distribution}
\end{figure}

@@

Figure of CK+ distribution with neutral images.

@@

\subsubsection{Convolutional Layer}
The convolutional layer is the core building block of a CNN. Each layer is initialized with a set of $n$ random two-dimensional filter matrices (eg 3x3 pixels) and a pixel-stride. When an image is put into the convolutional layer, each of the filters is moved across the height and width of the image, calculating a dot product between the filter matrix and the current section of the image. The resulting matrices of dot products are called feature maps. To introduce non-linearity to the operation, a ReLu activation function $f(n) = max(0, n)$ is used on the feature-maps element-wise. The filters in the convolutional layers are trained using a backpropagation algorithm. Intuitively, filters activate when they see different types of visual features, such as vertical or diagonal edges on the lower layers or, in the top convolutional layers, more complex patterns like eyebrows or mouths.

>>>>

\begin{figure}[H]
	\includegraphics[width=0.48\textwidth]{fer_examples}
	\caption{FER-2013 training samples}
\end{figure}

@@

\begin{figure}[H]
	\includegraphics[width=0.48\textwidth]{ferplus_distribution}
	\caption{FER-2013 dataset class distribution}
\end{figure}

@@

\begin{figure}[H]
	\includegraphics[width=0.48\textwidth]{ckplus_examples}
	\caption{Posed facial expressions from the CK+ dataset}
\end{figure}

@@

\subsubsection{Convolutional Layer}
The convolutional layer is the core building block of a CNN. Each layer is initialized with a set of $n$ random two-dimensional filter matrices (eg 3x3 pixels) and a pixel-stride. When an image is put into the convolutional layer, each of the filters is moved across the height and width of the image, calculating a dot product between the filter matrix and the current section of the image. The resulting matrices of dot products are called feature maps. To introduce non-linearity to the operation, a ReLu activation function $f(n) = max(0, n)$ is used on the feature-maps element-wise. The filters in the convolutional layers are trained using a backpropagation algorithm. Intuitively, filters activate when they see different types of visual features, such as vertical or diagonal edges on the lower layers or, in the top convolutional layers, more complex patterns like eyes or mouths.
